\Large Out title here

### 2012-09-14 proposal/proposal.tex
proposal update

\title{\Large Out title here}
\author{\small Mattijs Meiboom, Robin Mills, Tijn Schouten, and Spyros Ioakeimidis}
\date{\small \today}

@@

>>>>

\title{\Large Out title here}
\author{\small Mattijs Meiboom (student number), Robin Mills (student number)\\
			\small Tijn Schouten (student number), Spyros Ioakeimidis (2144603)}
\date{\small \today}

@@

This project is about ...

\section{Application}

Explain how you get data or simulator, how many examples, how many inputs, outputs, whether it is an RL, classification, or regression problem.

\section{Methods}

Explain the methods that you will compare. Identify the learning algorithm and the optimisation method.

\section{Setup of Experiments}

\section{Programming Language}

The chosen programming language is Python. We have chosen Python because ...

\section{Planning}

Describe the different phases and the planning deadlines (until November)
